Medical Concept Extraction

### 2012-12-16 paper/paper.tex
Updating reference to high dimensional challenge.
machine learning intro

Talk about multi-class classification

>>>>

Our system addresses the particular challenge of assigning concept labels to terms in medical records, but the task of assigning labels from multiple classes over a set of entries is a classic machine learning problem. Multi-class classification algorithms assign labels to input data entries using a model trained on a data set of pre-labeled observations. There are countless methods that support multi-class classification--for the purpose of this work, we employ three well-known strategies (Support Vector Machines, Linear Regression, and Conditional Random Fields) and compare their respective accuracies given our data sets and chosen features (section 4).
